---
title: "Regression"
author: "Scott Stoltzman"
date: "6/3/2019"
output: html_document
---

```{r}
library(tidyverse)
library(ggiraphExtra)
library(broom)
library(MASS)
library(ISLR)
```

### Explore your data set  
Take a look in your `Help` panel (in RStudio) to see the descriptions of the fields
```{r}
?Boston
```

### View your data
```{r}
data = as_tibble(Boston)
head(data)
```

### We will attempt to model the `medv` data - the median value of owner-occupied homes (in $1000s)

Plot the `lstat` on the x and `medv` on the y axis in a scatter plot.
```{r}
data %>%
  ggplot() + # Fix this line
  geom_() # Fix this line
```


### Build a model to predict `medv`
Do single linear regression utilizing `lm` 
```{r}
model_1 = lm( ~ , data = data) # Fix this line
model_1
```


### Show a better description of the model
```{r}
summary(model_1)
```


### Interpret what your results above mean:

< Homework >







### Can you display the confidence intervals?
```{r}
confint(model_1)
```

### Interpret what your results above mean:

< Homework >





### Predict points for lstat values of c(5, 10, 15)
```{r}
predict_points = tibble(lstat = ) # Fix this line
predict(model_1, , interval="confidence") # Fix this line
```


### Plot your first model
```{r}
ggPredict(model_1)
```


### Create a model using both `lstat` and `age`
```{r}
model_2 = # Fix this line
summary(model_2)
```


### Interpret what your results above mean:

< Homework >



### Create a model using all variables as predictors
```{r}
model_3 = # Fix this line
summary(model_3)
```

### Interpret what your results above mean:

< Homework >



### How do these numbers compare with those from `model_2` ?

< Homework >



### Create a model with an interaction term
Use `lstat` and `age` to predict `medv`
```{r}
model_4 = # Fix this line
summary(model_4)
```


### Interpret what your results above mean:

< Homework >




### Create a model using `lstat` and `lstat ^ 2`
```{r}
# have to use I() because ^ means something in formula
model_5 = # Fix this line
summary(model_5)
```


### Interpret what your results above mean:

< Homework >


### Is your model still linear?

< Homework >




### Plot your model's fitted values  
The tibble `data_model` has been created for you with the predictions in a column called `medv_predictions`
```{r}
data_model = data %>%
  mutate(medv_predictions = fitted(model_5))

data_model %>%
  ggplot(aes(x=lstat)) +
  geom_point(aes(y=medv)) + 
  geom_point(aes(y=medv_predictions), color='red')
```

### Interpret what your results above mean:

< Homework >
